Comparing probabilistic accounts of probability judgments

### 2021-10-27 paper-rmd/paper-papaja.Rmd
initial submission 2

authornote: |
 This manuscript is pre-print that has not yet been peer reviewed (October 27, 2021). This study was not preregistered.

@@

Bayesian theories of cognition offer a unified formal framework for cognitive science [@tenenbaum.etal2011] that has had remarkable explanatory successes across domains, including in perception [e.g. @kersten.etal2004], memory [e.g. @anderson1991], language [e.g. @xu.tenenbaum2007], and reasoning [e.g. @lu.etal2012]. At the heart of the Bayesian project is the idea that cognition is fundamentally probabilistic: that people reason according to subjective degrees of belief which follow the laws of probability and, in particular, that they are revised in light of evidence according to Bayes' Rule. It is somewhat embarrassing then, that that these theories have often been accused of failing to describe human "beliefs" of the simple and everyday sort, such as beliefs like "it will rain tomorrow", "vaccines are safe," or "this politician is trustworthy".

>>>>

authornote: |
 This manuscript has not yet been peer-reviewed. This study was not preregistered.

@@

Bayesian theories of cognition offer a unified formal framework for cognitive science [@tenenbaum.etal2011] that has had remarkable explanatory successes across domains, including in perception [e.g. @kersten.etal2004], memory [e.g. @anderson1991], language [e.g. @xu.tenenbaum2007], and reasoning [e.g. @lu.etal2012]. At the heart of the Bayesian project is the idea that cognition is fundamentally probabilistic: that people reason according to subjective degrees of belief which follow the laws of probability and, in particular, that they are revised in light of evidence according to Bayes' Rule. It is somewhat embarrassing then, that these theories have often been accused of failing to describe human "beliefs" of the simple and everyday sort, such as beliefs like "it will rain tomorrow", "vaccines are safe," or "this politician is trustworthy".

### 2021-10-27 paper-rmd/paper-papaja.tex
initial submission 2

This manuscript is pre-print that has not yet been peer reviewed (October 27, 2021). This study was not preregistered.

@@

Bayesian theories of cognition offer a unified formal framework for cognitive science \autocite{tenenbaum.etal2011} that has had remarkable explanatory successes across domains, including in perception \autocite[e.g.][]{kersten.etal2004}, memory \autocite[e.g.][]{anderson1991}, language \autocite[e.g.][]{xu.tenenbaum2007}, and reasoning \autocite[e.g.][]{lu.etal2012}. At the heart of the Bayesian project is the idea that cognition is fundamentally probabilistic: that people reason according to subjective degrees of belief which follow the laws of probability and, in particular, that they are revised in light of evidence according to Bayes' Rule. It is somewhat embarrassing then, that that these theories have often been accused of failing to describe human ``beliefs'' of the simple and everyday sort, such as beliefs like ``it will rain tomorrow'', ``vaccines are safe,'' or ``this politician is trustworthy''.

>>>>

This manuscript has not yet been peer-reviewed. This study was not preregistered.

@@

Bayesian theories of cognition offer a unified formal framework for cognitive science \autocite{tenenbaum.etal2011} that has had remarkable explanatory successes across domains, including in perception \autocite[e.g.][]{kersten.etal2004}, memory \autocite[e.g.][]{anderson1991}, language \autocite[e.g.][]{xu.tenenbaum2007}, and reasoning \autocite[e.g.][]{lu.etal2012}. At the heart of the Bayesian project is the idea that cognition is fundamentally probabilistic: that people reason according to subjective degrees of belief which follow the laws of probability and, in particular, that they are revised in light of evidence according to Bayes' Rule. It is somewhat embarrassing then, that these theories have often been accused of failing to describe human ``beliefs'' of the simple and everyday sort, such as beliefs like ``it will rain tomorrow'', ``vaccines are safe,'' or ``this politician is trustworthy''.
